%------------------------
% Arkadip Das Resume
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[colorlinks=true, urlcolor=black]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section format
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{#2}
}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4}
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[2]{
\item \small{\textbf{#1}: #2}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------

\begin{center}
{\huge \textbf{ARKADIP DAS}}\\[6pt]

\href{mailto:arkadip671@gmail.com}{arkadip671@gmail.com} \;\textbar\;
+91 7003986728 \;\textbar\;
\underline{\href{https://portfolio-arkade.vercel.app/}{Portfolio}} \;\textbar\;
\underline{\href{https://www.linkedin.com/in/arkadip-das-628a02278/}{LinkedIn}} \;\textbar\;
\underline{\href{https://github.com/notArkade}{GitHub}}

\end{center}

%-----------SUMMARY-----------------

\section{Summary}

Software Developer specializing in Artificial Intelligence and Machine Learning with experience building scalable web applications integrated with intelligent systems. Skilled in React.js, Next.js, Python, and Express.js with strong experience in API integration, responsive design, and modern UI development. Passionate about developing AI-powered digital products and data-driven applications that enhance user experience and performance.

%-----------TECHNICAL SKILLS-----------------

\section{Technical Skills}

\resumeSubHeadingListStart

\resumeSubItem{Programming Languages}{Python, JavaScript, C++, C\#, SQL}

\resumeSubItem{Frontend Development}{React.js, Next.js, HTML, CSS, Tailwind CSS, Responsive Design}

\resumeSubItem{Backend / Frameworks}{Express.js, REST APIs, .NET}

\resumeSubItem{AI / Data Libraries}{NumPy, Pandas}

\resumeSubItem{Developer Tools}{Git, GitHub, Figma, n8n, Microsoft Power Apps}

\resumeSubItem{Design Tools}{Adobe Premiere Pro, Adobe Illustrator}

\resumeSubHeadingListEnd

% %-----------RELEVANT COURSEWORK-----------------

% \section{Relevant Coursework}

% Machine Learning, Artificial Intelligence, Data Structures and Algorithms, 
% Database Management Systems, Computer Networks, Operating Systems

%-----------EDUCATION-----------------

\section{Education}

\resumeSubHeadingListStart

\resumeSubheading
{Bennett University}{Greater Noida, India}
{B.Tech in Computer Science Engineering (AI \& ML) | CGPA: 8.36}{2023 -- Present}

\resumeSubheading
{Delhi Public School, Ruby Park}{Kolkata, India}
{Class XII | Percentage: 77.8\%}{2022}

\resumeSubheading
{Delhi Public School, Ruby Park}{Kolkata, India}
{Class X | Percentage: 94.6\%}{2020}

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------

%-----------PROJECTS-----------------

\section{Projects}

\resumeSubHeadingListStart

\item
\textbf{Re:Write} \hfill \textit{Next.js, Tailwind CSS, Gemini API, Clerk, Supabase}
\resumeItemListStart
\resumeItem{}{An AI web app that turns long-form content (blogs, scripts) into short social media posts (Instagram, X, LinkedIn).}
\resumeItem{}{Built with Next.js, Tailwind CSS, and powered by the Google GenAI API for content generation.}
\resumeItem{}{Secured with Clerk for authentication and connected to Supabase for data management.}
\resumeItemListEnd

\item
\textbf{Bloomify} \hfill \textit{React.js, Tailwind CSS}
\resumeItemListStart
\resumeItem{}{Developed a flower marketplace platform enabling sellers to manage product listings and seasonal inventory.}
\resumeItem{}{Implemented an AI-based inventory prediction system to forecast seasonal demand and improve stock planning.}
\resumeItem{}{Built a fully responsive frontend using React and Tailwind CSS with a focus on clean UI and user experience.}
\resumeItemListEnd

\item
\textbf{The Movie Project} \hfill \textit{React.js, Tailwind CSS, Appwrite}
\resumeItemListStart
\resumeItem{}{Built a movie discovery web application that allows users to search and explore trending films.}
\resumeItem{}{Integrated third-party APIs to retrieve real-time movie data and dynamically update UI components.}
\resumeItem{}{Improved application performance by optimizing API requests and frontend rendering.}
\resumeItemListEnd

\item
\textbf{Sentinel} \hfill \textit{React.js, Python, Machine Learning}
\resumeItemListStart
\resumeItem{}{Developed a machine learning model to detect anomalous network traffic for intrusion detection.}
\resumeItem{}{Built backend APIs for real-time threat classification and monitoring.}
\resumeItem{}{Improved detection accuracy using feature engineering and data preprocessing techniques.}
\resumeItemListEnd

\resumeSubHeadingListEnd
%-----------ACHIEVEMENTS-----------------

\section{Achievements}

\begin{itemize}

\item \textbf{Runner-Up}, Gen AI Hackathon – Rishihood University (2025) among 50+ teams for building a generative AI-powered content automation platform.

\item \textbf{Shortlisted Team}, Designathon – Manipal University Jaipur (2026) for UX research, wireframing, and prototype design.

\item Participant, Hackaccino Hackathon – Bennett University (2024) developing a digital hub for student engagement in college festivals.

\end{itemize}


%-----------LANGUAGES-----------------

\section{Languages}

English, Hindi, Bengali

\end{document}